---
title: "Regression"
author: "Bret McNamee"
date: "11/14/2019"
output: html_document
---
# This hunk of code loads all of our datasets from our index.rmd file
```{r}
suppressMessages(library("tidyverse"))
suppressMessages(library("knitr"))
purl("insights.Rmd", output = "part1.r")
source("part1.r")
```
# This adds the avg ratings to the Person table, that was precalculated in the previous file
```{r}

Person <- dplyr::left_join(Person, newdf, by = "pseudonym")
```
# This code splits up our Person table so that 75% is put into the train variable and the remaining 25% is put into our test variable
These are used for creating our model and seeing how accurate it is
```{r}

set.seed(86) 
 
sample <- sample.int(n = nrow(Person), 
                     size = floor(.75*nrow(Person)), # Selecting 70% of data
                     replace = F)
 
train <- Person[sample, ]
test  <- Person[-sample, ]

```

# This creates the model using our training data
After wittling down our IV we determined that when year_born is our DV the only IV that generates a p-value below the 0.05 threshold is academic_lvl

```{r}
model <- lm(year_born~academic_level, train)
summary(model)
```

# Here we are using our test data to see how accurate our model is at predicting age.

```{r}
predictions <- model %>% predict(test)

```